\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeTitleItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://danielsmith.io/}{\Large Daniel Smith}} & Email : \href{mailto:daniel@danielsmith.io}{daniel@danielsmith.io}\\
  \href{https://danielsmith.io/}{https://danielsmith.io} & Github: \href{https://github.com/danielsmith4483/}{github.com/danielsmith4483}\\
  & Linkedin: \href{https://www.linkedin.com/in/danielsmith4483/}{linkedin.com/in/danielsmith4483}\\
  & Current location: Slidell, LA (able to relocate) \\
  & Mobile : +1-601-410-4483
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Southern Mississippi}{Hattiesburg, MS}
      {Master of Science in Computer Science;  GPA: 3.913}{Aug. 2015 -- Aug. 2016}
    \resumeSubheading
      {The University of Southern Mississippi}{Hattiesburg, MS}
      {Bachelor of Science in Computer Science;  GPA: 3.931}{May 2013 -- May 2015}
    \resumeSubheading
      {Jones County Junior College}{Ellisville, MS}
      {Associate of Applied Science in Information System Technology;  GPA: 4.000}{Aug. 2011 -- May 2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Naval Research Laboratory}{Stennis Space Center, MS}
      {Software Engineer}{Jan. 2017 - Present}
      \resumeItemListStart
        \resumeItem
        	{Developed various Qt plugins and functionality for projects involving mine warfare and post-mission analysis.}
        \resumeItem
        	{Participated in design discussions for Qt client applications supported by Java microservices.}
        \resumeItem
        	{Groomed and later executed stories and bug tickets in a product backlog using scrum practices.}
        \resumeItem
        	{Made product decisions among engineering team with minimal oversight from business while respecting project requirements/demands.}
        \resumeItem
        	{Reviewed code for feature branches and issued/accepted pull requests for integration branches.}
        \resumeItem
        	{Continuously improved development practices and helped team devise more efficient methods for collaboration and testing.}
      \resumeItemListEnd

    \resumeSubheading
      {The University of Southern Mississippi}{Hattiesburg, MS}
      {Software Developer}{Mar. 2014 - Dec. 2016}
      \resumeItemListStart
        \resumeItem
          {Designed and developed a content delivery framework for university department apps using Objective-C.}
        \resumeItem
          {Implemented networking libraries for background content updates for mobile apps.}
        \resumeItem
          {Created a content management web app using AngularJS.}
        \resumeItem
          {Helped manage app testing practices using TestFlight.}
        \resumeItem
          {Participated in the delivery of apps to the iTunes App Store.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeTitleItem{danielsmith.io}
    	{Portfolio website built on preact with optimizations for first meaningful paint and time to interactive. Developed using Preact.}
    \resumeTitleItem{Barbell Ninja}
    	{Progressive Web App to help optimize barbell plate unracking/reracking in a gym setting. Developed using React.}
    \resumeTitleItem{max-rep}
    	{N-Rep and One-Rep Max calculator implemented as an Node.js module for use by third parties in logger/calculator apps. Dependency for Barbell Ninja.}
  \resumeSubHeadingListEnd

\section{Programming Skills (strongest first)}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, JavaScript, Python, Ruby, Objective-C, SQL}
      \hfill
    }
    \item{
      \textbf{Technologies}{: React.js, Node.js, CSS, Redux, Google Cloud Platform, Express, Electron, React Native, Webpack, Vue.Js}
   	}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}